Symbolic Weighted Language Models and\\ Parsing over Infinite Alphabets

### 2021-07-02 introduction.tex
modifs Lydia

Various extensions of language models for handling infinite alphabets have been studied.
%words carrying data values in an infinite domain (e.g. integers) e.g. data processing 
For instance, some automata with memory extensions 
allow restricted storage and comparison of input symbols, 
%and correspond with logics, 
(see~\cite{Segoufin06csl} for a survey),
\mynote{register: skip refs and details, add Mikolaj recent}
with pebbles for marking positions~\cite{NevenSchwentickVianu04FSMinfinite}, 
registers~\cite{KaminskiFrancez94}, 
or %computations in 2 steps
the possibility to compute on subsequences 
with the same attribute values~\cite{Bojanczyk11FO2}. % data words automata.
%
%for the and verification of infinite state systems 
%(model checkers: alphabet = long bit-vectors)
%...For the representation of  in model checking, verification and 
%
The automata at the core of model checkers
compute on input symbols represented by large bitvectors~\cite{Vardi07ciaa} %\cite{BaierKatoen08MC}
(sets of assignments of Boolean variables) %propositional variables)
and in practice,  %implementation
each transition accepts a set of such symbols (instead of an individual symbol), 
represented by Boolean formula or Binary Decision Diagrams.
%
Following a similar idea, % and generalizing,
in symbolic automata (\SA)~\cite{dAntoniVeanes17CAV,dAntoni21CACM}, 
the transitions are guarded by predicates over infinite alphabet domains.
With appropriate closure conditions on the sets of such predicates, % (alphabet theories), 
all the good properties enjoyed by automata over finite alphabets are preserved.

@@

\mynote{chap. intersection in~\cite{GruneJacobs08parsing}} 

@@

% First one general edit-distance is defined by a weighted word 
% transducer~\cite{Mohri}
% %Symbolic automata transducers are extended models~\cite{VeanesdAntoniJACM}
% %dealing with infinite set of input symbols...
% value in a semiring...
\mynote{expressiveness: VPA have restricted equality test. 
        comparable to pebble automata? $\to$ conclusion}

>>>>

Various extensions of language models for handling infinite alphabets have been studied.
%words carrying data values in an infinite domain (e.g. integers) e.g. data processing 
For instance, some automata with memory extensions 
allow restricted storage and comparison of input symbols, 
%and correspond with logics, 
(see~\cite{Segoufin06csl} for a survey),
\florent{register: skip refs and details, add Mikolaj recent}
with pebbles for marking positions~\cite{NevenSchwentickVianu04FSMinfinite}, 
registers~\cite{KaminskiFrancez94}, 
or %computations in 2 steps
the possibility to compute on subsequences 
with the same attribute values~\cite{Bojanczyk11FO2}. % data words automata.
%
%for the and verification of infinite state systems 
%(model checkers: alphabet = long bit-vectors)
%...For the representation of  in model checking, verification and 
%
The automata at the core of model checkers
compute on input symbols represented by large bitvectors~\cite{Vardi07ciaa} %\cite{BaierKatoen08MC}
(sets of assignments of Boolean variables) %propositional variables)
and in practice,  %implementation
each transition accepts a set of such symbols (instead of an individual symbol), 
represented by Boolean formula or Binary Decision Diagrams.
%
Following a similar idea, % and generalizing,
in symbolic automata (\SA)~\cite{dAntoniVeanes17CAV,dAntoni21CACM}, 
the transitions are guarded by predicates over infinite alphabet domains.
With appropriate closure conditions on the sets of such predicates, % (alphabet theories), 
all the good properties enjoyed by automata over finite alphabets are preserved.

@@

\florent{chap. intersection in~\cite{GruneJacobs08parsing}} 

@@

% First one general edit-distance is defined by a weighted word 
% transducer~\cite{Mohri}
% %Symbolic automata transducers are extended models~\cite{VeanesdAntoniJACM}
% %dealing with infinite set of input symbols...
% value in a semiring...
\florent{expressiveness: VPA have restricted equality test. 
        comparable to pebble automata? $\to$ conclusion}
